Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-01-15 ms/ms06_floats.tex
ENH added marker genes

% full size table is table
\begin{table}[!tbp]
\centering
\scriptsize
%\hline
\csvreader[separator=tab,
tabular=crclcp{0.4\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Pos (hg38) & \bfseries Cytoband & \bfseries RSID & \bfseries Marker & \bfseries GWAS Categories\\\hline,
]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_ms.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
%\hline
%
\vspace{15pt}
%
\caption{Example eQTLs involved in four GWAS categories in different cytobands.
The whole list is given in the Supplementary files.
The gene marker is the eQTL gene with the highest PubMed publication count.}
\label{tab:pleitropic_variants}
\end{table}

@@

% full size table is table
\begin{table}[!tbp]
\centering
\scriptsize
%\hline
\csvreader[
separator=tab,
tabular=p{0.02\textwidth}p{0.09\textwidth}p{0.09\textwidth}p{0.05\textwidth}p{0.09\textwidth}p{0.09\textwidth}p{0.45\textwidth},
head,
table head=\bfseries Chr. & \bfseries Start & \bfseries End & \bfseries Cytob. & \bfseries Pleio RSID & \bfseries Pleio pos. & \bfseries GWAS Categories\\\hline,
]{\floatRelativePath/cmpt_pleiotropic_regions.py/100000/region_window_ms.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolv\ & \csvcolvi\ & \csvcoliv\ & \csvcolii\ & \csvcoliii\ & \csvcolvii}% specify your coloumns here
%\hline
%
\vspace{15pt}
\caption{Pleiotropic regions involving 6 or more GWAS classes. These regions were built with a sliding window of 1e5 nt. Genomic coordinates are given for the hg38 assembly.}\label{tab:pleiotropic_regions}
\end{table}

>>>>

% full size table is table
\begin{table}[!tbp]
\centering
\scriptsize
%\hline
\csvreader[separator=tab,
tabular=crclcp{0.4\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Pos (hg38) & \bfseries Cytoband & \bfseries RSID & \bfseries Marker eQTL gene& \bfseries GWAS Categories\\\hline,
]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_ms.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
%\hline
%
\vspace{15pt}
%
\caption{Example eQTLs involved in four GWAS categories in different cytobands.
The whole list is given in the Supplementary files.
The gene marker is the eQTL gene with the highest PubMed publication count.}
\label{tab:pleitropic_variants}
\end{table}

@@

% full size table is table
\begin{table}[!tbp]
\centering
\scriptsize
%\hline
\csvreader[
separator=tab,
tabular=p{0.05\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.5\textwidth},
head,
table head=\bfseries Chr. & \bfseries Start & \bfseries End & \bfseries Cytob. & \bfseries Marker eQTL gene & \bfseries GWAS Categories\\\hline,
]{\floatRelativePath/cmpt_pleiotropic_regions.py/100000/region_window_ms.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
%\hline
%
\vspace{15pt}
\caption{Pleiotropic regions involving 6 or more GWAS classes. These regions were built with a sliding window of 1e5 nt. Genomic coordinates are given for the hg38 assembly.}\label{tab:pleiotropic_regions}
\end{table}
